Motional Quantum Ground-State Cooing of a Single Sodium Atom

### 2017-05-26 presentations/na_cool_paper/paper.tex
[presentations/na_cool_paper] include figures that needs to be changed in the same directory under imgs/temp
[presentations/na_cool_paper] Fix figure 1

\begin{figure*}
  \includegraphics[height=6.5cm]{imgs/Na_RSC_schematic.pdf}
  \includegraphics[height=6.5cm]{sequence.pdf}
  \caption{(A) Energy diagram. D1 OP
    (B) Beam directions and polarizations
    (C) Sequence description
    \label{f-setup}}
\end{figure*}

@@

<WIP>

Finally, the deep trap that is needed to trap and image single Sodium atom also creates
a very large AC Stark shift in the excited state.

% impossible to load without switching
% The same effect also happens on OP causing
% *   cannot address atom in different position at the same time
% *   breakdown of excited state HF structure
% use switching

@@

\begin{figure*}
  \includegraphics[width=8cm]{imgs/spectrum_r.png}
  \includegraphics[width=8cm]{../../experiments/rabi_flop/imgs/fit_20170409_r2_0_ba.png}
  \caption{(A) (B) \label{f-radial}}
\end{figure*}

@@

\begin{figure*}
  \includegraphics[width=8cm]{imgs/spectrum_a1.png}
  \includegraphics[width=8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_0_ba.png}
  \caption{(A) (B) \label{f-axial}}
\end{figure*}

As mentioned previously, the axial direction is much less confined and therefore has a much higher
effective Lamb-Dicke parameter of $\sqrt{n}\eta_{Raman1}\approx2.4$. The Raman spectrum before applying Raman sideband cooling is shown in figure \ref{f-axial}A where we can see clearly resolved Raman cooling sidebands up to the 8th order suggesting that we have many vibrational states populated in this direction.

>>>>

\begin{figure*}
  \includegraphics[height=6cm]{imgs/Na_RSC_schematic.pdf}
  \includegraphics[height=5cm]{sequence.pdf}
  \caption{(A) Energy diagram. D1 OP
    (B) Beam directions and polarizations
    (C) Sequence description
    \label{f-setup}}
\end{figure*}

@@

Finally, the deep trap that is needed to trap and image single Sodium atom also creates
a very large AC Stark shift in the excited state. For the trap depth we are using, the
light shift in the center of the trap is as large as $300MHz$.
In additional to creating a large and position dependent detuning for the optical pumping light,
it also mixes the excited state state hyperfine levels,
affecting the branching ratio and increasing the number of photons needed during optical pumping.
Similar to our loading and imaging process [???], we solve this issue by switching the
trapping light at $3MHz$ during the whole cooling sequence.
Due to the large light shift, the optical pumping is effectively off when the trap light is on.
Since the atom can only be addressed by the optical pumping light when the trap light is off,
the effect of light shift on optical pumping fidelity is suppressed.

@@

\begin{figure*}
  \includegraphics[width=8cm]{imgs/spectrum_r.png}
  \includegraphics[width=8cm]{imgs/temp/fit_20170409_r2_0_ba.png}
  \caption{(A) (B) \label{f-radial}}
\end{figure*}

@@

\begin{figure*}
  \includegraphics[width=8cm]{imgs/spectrum_a1.png}
  \includegraphics[width=8cm]{imgs/temp/fit_20170409_a1_0_ba.png}
  \caption{(A) (B) \label{f-axial}}
\end{figure*}

As mentioned previously, the axial direction is much less confined and therefore has a much higher
effective Lamb-Dicke parameter of $\sqrt{n}\eta_{Raman1}\approx2.4$. The Raman spectrum before applying Raman sideband cooling is shown in figure \ref{f-axial}A where we can see clearly resolved Raman cooling sidebands up to the eighth order suggesting that we have many vibrational states populated in this direction.

### 2017-05-26 presentations/na_cool_paper/sequence.tex
[presentations/na_cool_paper] Fix figure 1

  \begin{scope}
    \clip (4.6, -6.5) rectangle (17.8, 3.5);
    %% Pulse mark
    \foreach \i in {0,...,7} {
      \draw[gray!20, line width=2] (2.8*\i, 1.8) -- (2.8*\i, -6.0);
      \draw[gray!20, line width=2] (2.8*\i+1.9, 1.8) -- (2.8*\i+1.9, -6.0);
    }

    %% Tweezer
    \draw[line width=1.5,purple] (0, 2) -- (22.4, 2);
    \foreach \i in {0,...,99} {
      \filldraw[line width=1,purple] (\i*22.4/100, 2) rectangle (\i*22.4/100+0.06, 3.5);
    }

    %% Axial
    \foreach \i in {0,...,7} {
      \fill[blue!30]
      plot[draw,samples=200,domain={2.8*\i}:{2.8*\i+1.6},variable=\x] ({\x}, {sin((\x-2.8*\i) * 112.5)^4})
      -- cycle;
      \draw[line width=1,blue] plot[domain={2.8*\i}:{2.8*\i+1.6},variable=\x]
      ({\x}, {sin((\x-2.8*\i) * 112.5)^4}) -- (2.8*\i + 2.8, 0);
    }
    \foreach \i in {0,...,3} {
      \path (5.6*\i + 0.8, 1) node[above,blue,align=center] {\textbf{$n$-th}\\\textbf{order}};
      \path (5.6*\i + 3.6, 1) node[above,blue,align=center] {\textbf{$(n-1)$-th}\\\textbf{order}};
    }

    %% Radial 2
    \foreach \i in {0,...,3} {
      \fill[red!30]
      plot[draw,samples=200,domain={5.6*\i+1.9}:{5.6*\i+2.5},variable=\x] ({\x}, {1.5*sin((\x-5.6*\i-1.9) * 300)^4 - 2})
      -- cycle;
      \draw[line width=1,red] (5.6*\i, -2) -- plot[domain={5.6*\i+1.9}:{5.6*\i+2.5},variable=\x]
      ({\x}, {1.5*sin((\x-5.6*\i-1.9) * 300)^4 - 2}) -- (5.6*\i+5.6, -2);
    }

    %% Radial 3
    \foreach \i in {0,...,3} {
      \fill[black!30]
      plot[draw,samples=200,domain={5.6*\i+4.7}:{5.6*\i+5.3},variable=\x] ({\x}, {1.5*sin((\x-5.6*\i-4.7) * 300)^4 - 4})
      -- cycle;
      \draw[line width=1,black] (5.6*\i, -4) -- plot[domain={5.6*\i+4.7}:{5.6*\i+5.3},variable=\x]
      ({\x}, {1.5*sin((\x-5.6*\i-4.7) * 300)^4 - 4}) -- (5.6*\i+5.6, -4);
    }

    %% OP
    \foreach \i in {0,...,7} {
      \filldraw[fill=orange!30,draw=orange,line width=1.2]
      (2.8*\i+1.58, -6) rectangle (2.8*\i+1.91, -4.5);
      \filldraw[fill=orange!30,draw=orange,line width=1.2]
      (2.8*\i+2.48, -6) rectangle (2.8*\i+2.81, -4.5);
    }
    \draw[line width=2,orange] (0,-6) -- (22.4,-6);
  \end{scope}

  \fill[white,path fading=fade img right] (16.8, -6.6) rectangle (17.81, 3.51);
  \fill[white,path fading=fade img right] (16.8, -6.6) rectangle (17.81, 3.51);
  \fill[white,path fading=fade img right] (16.8, -6.6) rectangle (17.81, 3.51);

  \fill[white,path fading=fade img left] (5.6, -6.6) rectangle (4.59, 3.51);
  \fill[white,path fading=fade img left] (5.6, -6.6) rectangle (4.59, 3.51);
  \fill[white,path fading=fade img left] (5.6, -6.6) rectangle (4.59, 3.51);

  \path (5.0, 2.3) node[left,purple,align=center] {\textbf{Tweezer}};
  \path (4.8, 0.5) node[left,blue,align=center] {\textbf{Axis 1}\\\textit{Axial}};
  \path (4.8, -1.5) node[left,red,align=center] {\textbf{Axis 2}\\\textit{Radial}};
  \path (4.8, -3.5) node[left,black,align=center] {\textbf{Axis 3}\\\textit{Radial}};
  \path (5.15, -5.5) node[left,orange,align=center] {\textbf{Optical}\\\textbf{pumping}};
  \draw[line width=2,orange,->] (5.6,-6) -- (17.8,-6) node[right, below] {\scalebox{2}{$t$}};

  %% Cycle mark
  \draw[decoration={brace,mirror,raise=3pt, amplitude=10pt},decorate,line width=2]
  (5.6,-6) -- node[below=15pt] {\scalebox{1.5}{One cooling cycle}} (16.8,-6);

>>>>

  \begin{scope}
    \clip (4.6, -2.1) rectangle (17.8, 3.5);
    %% Pulse mark
    \foreach \i in {0,...,7} {
      \draw[gray!20, line width=2] (2.8*\i, 1.5) -- (2.8*\i, -2.0);
      \draw[gray!20, line width=2] (2.8*\i+1.9, 1.5) -- (2.8*\i+1.9, -2.0);
    }

    %% Tweezer
    \draw[line width=1.5,purple] (0, 2.4) -- (22.4, 2.4);
    \foreach \i in {0,...,99} {
      \filldraw[line width=1,purple] (\i*22.4/100, 2.4) rectangle (\i*22.4/100+0.06, 3.5);
    }

    %% Axial
    \foreach \i in {0,...,7} {
      \fill[blue!30]
      plot[draw,samples=200,domain={2.8*\i}:{2.8*\i+1.6},variable=\x] ({\x}, {sin((\x-2.8*\i) * 112.5)^4})
      -- cycle;
      \draw[line width=1,blue] plot[domain={2.8*\i}:{2.8*\i+1.6},variable=\x]
      ({\x}, {sin((\x-2.8*\i) * 112.5)^4}) -- (2.8*\i + 2.8, 0);
    }
    \path[blue] (2.8*2+0.8, 0) node[below,align=center] {\textbf{Axis 1}\\\textit{Axial}};
    \foreach \i in {0,...,3} {
      \path (5.6*\i + 0.8, 1) node[above,blue,align=center] {\textbf{$n$-th}\\\textbf{order}};
      \path (5.6*\i + 3.6, 1) node[above,blue,align=center] {\textbf{$(n-1)$-th}\\\textbf{order}};
    }

    %% Radial 2
    \foreach \i in {0,...,3} {
      \fill[red!30]
      plot[draw,samples=200,domain={5.6*\i+1.9}:{5.6*\i+2.5},variable=\x] ({\x}, {1.5*sin((\x-5.6*\i-1.9) * 300)^4})
      -- cycle;
      \draw[line width=1,red] (5.6*\i, 0) -- plot[domain={5.6*\i+1.9}:{5.6*\i+2.5},variable=\x]
      ({\x}, {1.5*sin((\x-5.6*\i-1.9) * 300)^4}) -- (5.6*\i+5.6, 0);
    }
    \path[red] (5.6*1+2.2, 1.5) node[above,align=center] {\textbf{Axis 2}\\\textit{Radial}};

    %% Radial 3
    \foreach \i in {0,...,3} {
      \fill[black!30]
      plot[draw,samples=200,domain={5.6*\i+4.7}:{5.6*\i+5.3},variable=\x] ({\x}, {1.5*sin((\x-5.6*\i-4.7) * 300)^4})
      -- cycle;
      \draw[line width=1,black] (5.6*\i, 0) -- plot[domain={5.6*\i+4.7}:{5.6*\i+5.3},variable=\x]
      ({\x}, {1.5*sin((\x-5.6*\i-4.7) * 300)^4}) -- (5.6*\i+5.6, 0);
    }
    \path[black] (5.6*1+5.0, 1.5) node[above,align=center] {\textbf{Axis 3}\\\textit{Radial}};

    %% OP
    \foreach \i in {0,...,7} {
      \filldraw[fill=orange!30,draw=orange,line width=1.2]
      (2.8*\i+1.58, -2) rectangle (2.8*\i+1.91, -0.7);
      \filldraw[fill=orange!30,draw=orange,line width=1.2]
      (2.8*\i+2.48, -2) rectangle (2.8*\i+2.81, -0.7);
    }
    \draw[line width=2,orange] (0,-2) -- (22.4,-2);
  \end{scope}

  \fill[white,path fading=fade img right] (16.8, -2.2) rectangle (17.81, 3.51);
  \fill[white,path fading=fade img right] (16.8, -2.2) rectangle (17.81, 3.51);
  \fill[white,path fading=fade img right] (16.8, -2.2) rectangle (17.81, 3.51);

  \fill[white,path fading=fade img left] (5.6, -2.2) rectangle (4.59, 3.51);
  \fill[white,path fading=fade img left] (5.6, -2.2) rectangle (4.59, 3.51);
  \fill[white,path fading=fade img left] (5.6, -2.2) rectangle (4.59, 3.51);

  \path (5.0, 2.3) node[left,purple,align=center] {\textbf{Tweezer}};
  \path (4.8, 0.5) node[left,align=center] {\textbf{Raman}};
  \path (5.15, -1.5) node[left,orange,align=center] {\textbf{Optical}\\\textbf{pumping}};
  \draw[line width=2,orange,->] (5.6,-2) -- (17.8,-2) node[right, below] {\scalebox{2}{$t$}};

  %% Cycle mark
  \draw[decoration={brace,mirror,raise=3pt, amplitude=10pt},decorate,line width=2]
  (5.6,-2) -- node[below=15pt] {\scalebox{1.5}{One cooling cycle}} (16.8,-2);
